### 2016-12-01 paper/chapters/vae.tex
loss -> objective

\subsection{Loss function}
The loss function of the VAE consists of two terms, the negative log-likelihood or the reconstruction error $\mathcal{C}_{\mathrm{rec}}$ and the second term $\mathcal{C}_{\mathrm{KL}}$ serves as the regularizer.
We will discuss both terms in detail below.

>>>>

\subsection{Objective}
The objective function of the VAE consists of the reconstruction error and the regularizer.
%$\mathcal{L}$ learns both the encoder as well as the decoder with their respective parameters $\phi$ and $\theta$.
% probabilistic encoder $q_\phi(z|x)$ (produces z values from which x could've been generated)
% probabilistic decoder $p_\theta(x|z)$
We will discuss both terms in detail below.
